Advanced Normalization Tools (ANTS)

### 2009-06-05 Documentation/Tex/ants.tex
figs and minor updates
git-svn-id: https://advants.svn.sourceforge.net/svnroot/advants@10 fd2da0a4-d968-48df-9cb5-d8c496287cbf

\subsection{User/Label-Guided Normalization for Hippocampus Mapping}
See the link for details on hippocampus labeling:
\href{http://picsl.upenn.edu/ANTS/hipptutorial.php}{http://picsl.upenn.edu/ANTS/hipptutorial.php}.
\noindent{\bf Expectation-Based Point-Set Registration.}
Here, we apply the expectation-based point set registration method 
for mapping labeled points sets.   ITK-SNAP may be used to label 
images and exported segmentation images may be input to the 
PSE metric below, as labeled data.  The Frown and Smile data is used 
as example.  This data is available in the 
ANTS/Examples/Data/ directory.
\begin{verbatim}
ANTS 2 -o PSEtest  -i 91x70x55x40x30  -r Gauss[3,0.] -t SyN[0.3]  
   -m  PSE[Frown.nii,Smile.nii,Frown.nii,Smile.nii,1,0.2,11,0,25] 
    -m  MSQ[Frown.nii,Smile.nii,1,0] 
     --continue-affine 0  --number-of-affine-iterations 0

WarpImageMultiTransform  2 Frown.nii temp.nii -R Smile.nii
   -i PSEtestAffine.txt PSEtestInverseWarp.nii

WarpImageMultiTransform  2 Smile.nii temp2.nii -R Frown.nii 
    PSEtestWarp.nii PSEtestAffine.txt

>>>>

\subsection{User/Label-Guided Normalization for Hippocampus Mapping}
See the link for details on hippocampus labeling:
\href{http://picsl.upenn.edu/ANTS/hipptutorial.php}{http://picsl.upenn.edu/ANTS/hipptutorial.php}.
\noindent{\bf Expectation-Based Point-Set Registration.}
Here, we apply the expectation-based point set registration method 
for mapping labeled points sets.   ITK-SNAP may be used to label 
images and exported segmentation images may be input to the 
PSE metric below, as labeled data.  The Frown and Smile data is used 
as example.  This data is available in the 
ANTS/Examples/Data/ directory.
\begin{figure}
\label{fig:frown}
\includegraphics[width=0.45\textwidth]{Figures/frowntosmile.png}
\includegraphics[width=0.45\textwidth]{Figures/smiletofrown.png}
\itkcaption[Frown To Smile]{Expected output for the frown to smile 
shows a smooth, though large deformation.  The grids are overlaid on 
the deformed images. }
\end{figure}
\begin{verbatim}
ANTS 2 -o PSEtest  -i 91x70x55x40x30  -r Gauss[3,0.] -t SyN[0.2]
   -m  PSE[Frown.nii,Smile.nii,Frown.nii,Smile.nii,0.75,0.1,11,0,10] 
   -m  MSQ[Frown.nii,Smile.nii,1,0]    --number-of-affine-iterations 0

WarpImageMultiTransform  2 Frown.nii FrownToSmile.nii -R Smile.nii
   -i PSEtestAffine.txt PSEtestInverseWarp.nii

WarpImageMultiTransform  2 Smile.nii SmileToFrown.nii -R Frown.nii 
    PSEtestWarp.nii PSEtestAffine.txt
